---
title: "Untitled"
author: "Abanather Negusu & Claire Phibbs"
date: "2022-11-19"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
# Appendix Code

## Loading in Libraries 
```{r warning=FALSE}
# cleaning the memory
rm(list = ls())
# libraries
library(ggplot2)

library(tidyr)
library(plyr)
library(dplyr)
library(forecast)
library(lubridate)
library(data.table)
#install.packages('corrplot')
library(corrplot)
library(chron)
library(fpp2)
require(gridExtra)
```

## Loading in all 3 data sets
```{r}
Sales_df <- read.csv("/Users/clairephibbs/Desktop/ADS 506 Applied Time Series Analysis/Final Project/sales data-set.csv")

Feature_df <- read.csv("/Users/clairephibbs/Desktop/ADS 506 Applied Time Series Analysis/Final Project/Features data set.csv")

Stores_df <- read.csv("/Users/clairephibbs/Desktop/ADS 506 Applied Time Series Analysis/Final Project/stores data-set.csv")
```

### Sales Data
```{r}
# change the variable into appropriate type
Sales_df <-
  Sales_df %>%
  mutate(Store = as.factor(Store),
         Dept = as.factor(Dept),
         IsHoliday = as.factor(IsHoliday),
         Date = as.Date(Date, "%d/%m/%Y"))

# removing the nenagive sales
Sales_df <- Sales_df %>%
  filter(Weekly_Sales >= 0)
```

### Feature Data
```{r}
Feature_df <-
  Feature_df %>%
  mutate(Store = as.factor(Store),
         IsHoliday = as.factor(IsHoliday),
         Date = as.Date(Date, "%d/%m/%Y"))
```

### Combining Sales and Feature Data
```{r}
df <- Sales_df %>%inner_join(Feature_df) %>%
  select(c(1:7, 13:14), Weekly_Sales)
# attaching the data

attach(df)

# reformatting date to 2 digit years
df$Date <- as.character(df$Date, format = '%m/%d/%y')

```

### Store Data
```{r}
Stores_df <-
  Stores_df %>%
  mutate(Store = as.factor(Store))
```

## Exploratory Data Analysis (EDA):

#### From this point forwards only working with Store 1 data.

### Time Series Objects for the Weekly_Sales
```{r}
# separating departments of store 1 and creating time series objects 
store_1.1 <- df[1:143, ]
store_1.1_ts <- ts(store_1.1$Weekly_Sales, start = c(2010), frequency = 52)

store_1.2 <- df[144:286, ]
store_1.2_ts <- ts(store_1.2$Weekly_Sales, start = c(2010), frequency = 52)

store_1.3 <- df[287:429, ]
store_1.3_ts <- ts(store_1.3$Weekly_Sales, start = c(2010), frequency = 52)

store_1.4 <- df[430:572, ]
store_1.4_ts <- ts(store_1.4$Weekly_Sales, start = c(2010), frequency = 52)

store_1.5 <- df[573:715, ]
store_1.5_ts <- ts(store_1.5$Weekly_Sales, start = c(2010), frequency = 52)

store_1.6 <- df[715:857, ]
store_1.6_ts <- ts(store_1.6$Weekly_Sales, start = c(2010), frequency = 52)

store_1.7 <- df[858:1000, ]
store_1.7_ts <- ts(store_1.7$Weekly_Sales, start = c(2010), frequency = 52)

store_1.8 <- df[1001:1143, ]
store_1.8_ts <- ts(store_1.8$Weekly_Sales, start = c(2010), frequency = 52)

store_1.9 <- df[1144:1286, ]
store_1.9_ts <- ts(store_1.9$Weekly_Sales, start = c(2010), frequency = 52)

store_1.10 <- df[1287:1429, ]
store_1.10_ts <- ts(store_1.10$Weekly_Sales, start = c(2010), frequency = 52)

store_1.11 <- df[1430:1572, ]
store_1.11_ts <- ts(store_1.11$Weekly_Sales, start = c(2010), frequency = 52)

store_1.12 <- df[1573:1715, ]
store_1.12_ts <- ts(store_1.12$Weekly_Sales, start = c(2010), frequency = 52)

store_1.13 <- df[1716:1858, ]
store_1.13_ts <- ts(store_1.13$Weekly_Sales, start = c(2010), frequency = 52)
```

### Time Plots of Store 1 Department 1-13 Weekly Sales
```{r}
autoplot(store_1.1_ts) +
  labs(title = "Dept. 1 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.2_ts) +
  labs(title = "Dept. 2 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.3_ts) +
  labs(title = "Dept. 3 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.4_ts) +
  labs(title = "Dept. 4 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.5_ts) +
  labs(title = "Dept. 5 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.6_ts) +
  labs(title = "Dept. 6 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.7_ts) +
  labs(title = "Dept. 7 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.8_ts) +
  labs(title = "Dept. 8 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.9_ts) +
  labs(title = "Dept. 9 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.10_ts) +
  labs(title = "Dept. 10 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.11_ts) +
  labs(title = "Dept. 11 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.12_ts) +
  labs(title = "Dept. 12 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()

autoplot(store_1.13_ts) +
  labs(title = "Dept. 13 Time Plot Weekly_Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

### Scatter Plots of Each Departments Weekly_Sales vs. Unemployment/CPI/Temperature/Unemployment 
```{r}
scatter_1.1.1 <- ggplot(store_1.1, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.1.2 <- ggplot(store_1.1, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.1.3 <- ggplot(store_1.1, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.1.4 <- ggplot(store_1.1, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.1.1, scatter_1.1.2, scatter_1.1.3, scatter_1.1.4)

scatter_1.2.1 <- ggplot(store_1.2, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.2.2 <- ggplot(store_1.2, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.2.3 <- ggplot(store_1.2, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.2.4 <- ggplot(store_1.2, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.2.1, scatter_1.2.2, scatter_1.2.3, scatter_1.2.4)

scatter_1.3.1 <- ggplot(store_1.3, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.3.2 <- ggplot(store_1.3, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.3.3 <- ggplot(store_1.3, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.3.4 <- ggplot(store_1.3, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.3.1, scatter_1.3.2, scatter_1.3.3, scatter_1.3.4)

scatter_1.4.1 <- ggplot(store_1.4, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.4.2 <- ggplot(store_1.4, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.4.3 <- ggplot(store_1.4, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.4.4 <- ggplot(store_1.4, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.4.1, scatter_1.4.2, scatter_1.4.3, scatter_1.4.4)

scatter_1.5.1 <- ggplot(store_1.5, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.5.2 <- ggplot(store_1.5, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.5.3 <- ggplot(store_1.5, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.5.4 <- ggplot(store_1.5, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.5.1, scatter_1.5.2, scatter_1.5.3, scatter_1.5.4)

scatter_1.6.1 <- ggplot(store_1.6, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.6.2 <- ggplot(store_1.6, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.6.3 <- ggplot(store_1.6, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.6.4 <- ggplot(store_1.6, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.6.1, scatter_1.6.2, scatter_1.6.3, scatter_1.6.4)

scatter_1.7.1 <- ggplot(store_1.7, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.7.2 <- ggplot(store_1.7, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.7.3 <- ggplot(store_1.7, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.7.4 <- ggplot(store_1.7, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.7.1, scatter_1.7.2, scatter_1.7.3, scatter_1.7.4)

scatter_1.8.1 <- ggplot(store_1.8, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.8.2 <- ggplot(store_1.8, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.8.3 <- ggplot(store_1.8, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.8.4 <- ggplot(store_1.8, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.8.1, scatter_1.8.2, scatter_1.8.3, scatter_1.8.4)

scatter_1.9.1 <- ggplot(store_1.9, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.9.2 <- ggplot(store_1.9, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.9.3 <- ggplot(store_1.9, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.9.4 <- ggplot(store_1.9, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.9.1, scatter_1.9.2, scatter_1.9.3, scatter_1.9.4)

scatter_1.10.1 <- ggplot(store_1.10, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.10.2 <- ggplot(store_1.10, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.10.3 <- ggplot(store_1.10, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.10.4 <- ggplot(store_1.10, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.10.1, scatter_1.10.2, scatter_1.10.3, scatter_1.10.4)

scatter_1.11.1 <- ggplot(store_1.11, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.11.2 <- ggplot(store_1.11, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.11.3 <- ggplot(store_1.11, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.11.4 <- ggplot(store_1.11, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.11.1, scatter_1.11.2, scatter_1.11.3, scatter_1.11.4)

scatter_1.12.1 <- ggplot(store_1.12, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.12.2 <- ggplot(store_1.12, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.12.3 <- ggplot(store_1.12, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.12.4 <- ggplot(store_1.12, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.12.1, scatter_1.12.2, scatter_1.12.3, scatter_1.12.4)

scatter_1.13.1 <- ggplot(store_1.13, aes(x = Temperature, y = Weekly_Sales)) +
  ggtitle("Temperature vs Weekly Sales") +
  geom_point()

scatter_1.13.2 <- ggplot(store_1.13, aes(x = Fuel_Price, y = Weekly_Sales)) +
  ggtitle("Fuel Price vs Weekly Sales") +
  geom_point()

scatter_1.13.3 <- ggplot(store_1.13, aes(x = CPI, y = Weekly_Sales)) +
  ggtitle("CPI vs Weekly Sales") +
  geom_point()

scatter_1.13.4 <- ggplot(store_1.13, aes(x = Unemployment, y = Weekly_Sales)) +
  ggtitle("Unemployment vs Weekly Sales") +
  geom_point()

grid.arrange(scatter_1.13.1, scatter_1.13.2, scatter_1.13.3, scatter_1.13.4)
```

### Autocorrelation Plots of Weekly_Sales
```{r}
# department 1
acf(ts(store_1.1$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.1$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

#department 2
acf(ts(store_1.2$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.2$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 3
acf(ts(store_1.3$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.3$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 4
acf(ts(store_1.4$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.4$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 5
acf(ts(store_1.5$Weekly_Sales, start = c(2010), frequency = 52), lag =52)
pacf(ts(store_1.5$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 6
acf(ts(store_1.6$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.6$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 7
acf(ts(store_1.7$Weekly_Sales, start = c(2010), frequency = 52), lag =52)
pacf(ts(store_1.7$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 8
acf(ts(store_1.8$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.8$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 9
acf(ts(store_1.9$Weekly_Sales, start = c(2010), frequency = 52), lag =52)
pacf(ts(store_1.9$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 10
acf(ts(store_1.10$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.10$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 11
acf(ts(store_1.11$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.11$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 12
acf(ts(store_1.12$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.12$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)

# department 13
acf(ts(store_1.13$Weekly_Sales, start = c(2010), frequency = 52), lag = 52)
pacf(ts(store_1.13$Weekly_Sales, start = c(2010), frequency = 52), lag.max = 140)
```

## Data Cleaning:

### Identifying and replacing outliers 
```{r}
# using tsclean function, which identifies and replaced outliers 
store_1.1_clean <- tsclean(store_1.1_ts)
store_1.2_clean <- tsclean(store_1.2_ts)
store_1.3_clean <- tsclean(store_1.3_ts)
store_1.4_clean <- tsclean(store_1.4_ts)
store_1.5_clean <- tsclean(store_1.5_ts)
store_1.6_clean <- tsclean(store_1.6_ts)
store_1.7_clean <- tsclean(store_1.7_ts)
store_1.8_clean <- tsclean(store_1.8_ts)
store_1.9_clean <- tsclean(store_1.9_ts)
store_1.10_clean <- tsclean(store_1.10_ts)
store_1.11_clean <- tsclean(store_1.11_ts)
store_1.12_clean <- tsclean(store_1.12_ts)
store_1.13_clean <- tsclean(store_1.13_ts)
```

## Modeling:

### Partitioning Data

```{r}
# store 1 dept 1
training_1.1 <- window(store_1.1_clean, end = c(2012, 26))
validation_1.1 <- window(store_1.1_clean, start = c(2012, 27))

predictors_1.1 <- as.matrix(store_1.1["Temperature"][1:130,])

# store 1 dept 2
training_1.2 <- window(store_1.2_clean, end = c(2012, 26))
validation_1.2 <- window(store_1.2_clean, start = c(2012, 27))

predictors_1.2 <- as.matrix(store_1.2["Temperature"][1:130,])

# store 1 dept 3
training_1.3 <- window(store_1.3_clean, end = c(2012, 26))
validation_1.3 <- window(store_1.3_clean, start = c(2012, 27))

predictors_1.3 <- as.matrix(store_1.3["Temperature"][1:130,])

# store 1 dept 4
training_1.4 <- window(store_1.4_clean, end = c(2012, 26))
validation_1.4 <- window(store_1.4_clean, start = c(2012, 27))

predictors_1.4 <- as.matrix(store_1.4["Temperature"][1:130,])

 # store 1 dept 5
training_1.5 <- window(store_1.5_clean, end = c(2012, 26))
validation_1.5 <- window(store_1.5_clean, start = c(2012, 27))

predictors_1.5 <- as.matrix(store_1.5["Temperature"][1:130,])

# store 1 dept 6
training_1.6 <- window(store_1.6_clean, end = c(2012, 26))
validation_1.6 <- window(store_1.6_clean, start = c(2012, 27))

predictors_1.6 <- as.matrix(store_1.6["Temperature"][1:130,])

# store 1 dept 7
training_1.7 <- window(store_1.7_clean, end = c(2012, 26))
validation_1.7 <- window(store_1.7_clean, start = c(2012, 27))

predictors_1.7 <- as.matrix(store_1.7["Temperature"][1:130,])

# store 1 dept 8
training_1.8 <- window(store_1.8_clean, end = c(2012, 26))
validation_1.8 <- window(store_1.8_clean, start = c(2012, 27))

predictors_1.8 <- as.matrix(store_1.8["Temperature"][1:130,])

# store 1 dept 9
training_1.9 <- window(store_1.9_clean, end = c(2012, 26))
validation_1.9 <- window(store_1.9_clean, start = c(2012, 27))

predictors_1.9 <- as.matrix(store_1.9["Temperature"][1:130,])

# store 1 dept 10
training_1.10 <- window(store_1.10_clean, end = c(2012, 26))
validation_1.10 <- window(store_1.10_clean, start = c(2012, 27))

predictors_1.10 <- as.matrix(store_1.10["Temperature"][1:130,])

# store 1 dept 11
training_1.11 <- window(store_1.11_clean, end = c(2012, 26))
validation_1.11 <- window(store_1.11_clean, start = c(2012, 27))

predictors_1.11 <- as.matrix(store_1.11["Temperature"][1:130,])

# store 1 dept 12
training_1.12 <- window(store_1.12_clean, end = c(2012, 26))
validation_1.12 <- window(store_1.12_clean, start = c(2012, 27))

predictors_1.12 <- as.matrix(store_1.12["Temperature"][1:130,])

# store 1 dept 13
training_1.13 <- window(store_1.13_clean, end = c(2012, 26))
validation_1.13 <- window(store_1.13_clean, start = c(2012, 27))

predictors_1.13 <- as.matrix(store_1.13["Temperature"][1:130,])
```

#### Department 1 Models: 
```{r}
AutoArima_1.1 <- auto.arima(training_1.1, xreg = predictors_1.1) 
summary(AutoArima_1.1)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.1 <- Arima(training_1.1, xreg = predictors_1.1, order = c(0, 1, 3), seasonal = c(0, 1, 1))
summary(arima_1.1)

# prediction on the arima
new.predictors_1.1 <- as.matrix(store_1.1["Temperature"][131:143,])
forecast.arima.sales_1.1 <- forecast(arima_1.1, xreg = new.predictors_1.1)

# plot of forecasted values
autoplot(training_1.1, series = "Training") +
  autolayer(forecast.arima.sales_1.1, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.1, series = "Validation") +
  labs(title = "Dept. 1 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.1 <- store_1.1[1:130, 6]
linear_1.1 <- tslm(training_1.1 ~ trend + season + temp_1.1)
summary(linear_1.1)

# calculating RMSE
sqrt(mean(linear_1.1$residuals^2))

# forecasting 
temp.new_1.1 <- store_1.1[131:143, 6]
forecast.lm.sales_1.1 <- forecast(linear_1.1, temp.new_1.1, h = 13)
forecast.lm.sales_1.1

# plot of forecasted values
autoplot(training_1.1, series = "Training") +
  autolayer(forecast.lm.sales_1.1, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.1, series = "Validation") +
  labs(title = "Dept. 1 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 2 Models: 
```{r}
# Auto ARIMA model
AutoArima_1.2 <- auto.arima(training_1.2, xreg = predictors_1.2) 
summary(AutoArima_1.2)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.2 <- Arima(training_1.2, xreg = predictors_1.2, order = c(4, 1, 0), seasonal = c(1, 1, 1))
summary(arima_1.2)

# prediction on the arima
new.predictors_1.2 <- as.matrix(store_1.2["Temperature"][131:143,])
forecast.arima.sales_1.2 <- forecast(arima_1.2, xreg = new.predictors_1.2)
forecast.arima.sales_1.2

# plot of forecasted values
autoplot(training_1.2, series = "Training") +
  autolayer(forecast.arima.sales_1.2, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.2, series = "Validation") +
  labs(title = "Dept. 2 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.2 <- store_1.2[1:130, 6]
linear_1.2 <- tslm(training_1.2 ~ trend + season + temp_1.2)
summary(linear_1.2)

# calculating RMSE
sqrt(mean(linear_1.2$residuals^2))

# forecasting 
temp.new_1.2 <- store_1.2[131:143, 6]
forecast.lm.sales_1.2 <- forecast(linear_1.2, temp.new_1.2, h = 13)
forecast.lm.sales_1.2

# plot of forecasted values
autoplot(training_1.2, series = "Training") +
  autolayer(forecast.lm.sales_1.2, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.2, series = "Validation") +
  labs(title = "Dept. 2 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 3 Models: 
```{r}
# Auto ARIMA model
AutoArima_1.3 <- auto.arima(training_1.3, xreg = predictors_1.3) 
summary(AutoArima_1.3)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.3 <- Arima(training_1.3, xreg = predictors_1.3, order = c(0, 1, 3), seasonal = c(0, 1, 1))
summary(arima_1.3)

# prediction on the arima
new.predictors_1.3 <- as.matrix(store_1.3["Temperature"][131:143,])
forecast.arima.sales_1.3 <- forecast(arima_1.3, xreg = new.predictors_1.3)
forecast.arima.sales_1.3

# plot of forecasted values
autoplot(training_1.3, series = "Training") +
  autolayer(forecast.arima.sales_1.3, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.3, series = "Validation") +
  labs(title = "Dept. 3 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```
```{r}
# linear model
temp_1.3 <- store_1.3[1:130, 6]
linear_1.3 <- tslm(training_1.3 ~ trend + season + temp_1.3)
summary(linear_1.3)

# calculating RMSE
sqrt(mean(linear_1.3$residuals^2))

# forecasting 
temp.new_1.3 <- store_1.3[131:143, 6]
forecast.lm.sales_1.3 <- forecast(linear_1.3, temp.new_1.3, h = 13)
forecast.lm.sales_1.3

# plot of forecasted values
autoplot(training_1.3, series = "Training") +
  autolayer(forecast.lm.sales_1.3, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.3, series = "Validation") +
  labs(title = "Dept. 3 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 4 Models: 
```{r}
# Auto ARIMA model
AutoArima_1.4 <- auto.arima(training_1.4, xreg = predictors_1.4) 
summary(AutoArima_1.4)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.4 <- Arima(training_1.4, xreg = predictors_1.4, order = c(1, 1, 3), seasonal = c(0, 1, 1))
summary(arima_1.4)

# prediction on the arima
new.predictors_1.4 <- as.matrix(store_1.4["Temperature"][131:143,])
forecast.arima.sales_1.4 <- forecast(arima_1.4, xreg = new.predictors_1.4)

# plot of forecasted values
autoplot(training_1.4, series = "Training") +
  autolayer(forecast.arima.sales_1.4, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.4, series = "Validation") +
  labs(title = "Dept. 4 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```
```{r}
# linear model
temp_1.4 <- store_1.4[1:130, 6]
linear_1.4 <- tslm(training_1.4 ~ trend + season + temp_1.4)
summary(linear_1.4)

# calculating RMSE
sqrt(mean(linear_1.4$residuals^2))

# forecasting 
temp.new_1.4 <- store_1.4[131:143, 6]
forecast.lm.sales_1.4 <- forecast(linear_1.4, temp.new_1.4, h = 13)
forecast.lm.sales_1.4

# plot of forecasted values
autoplot(training_1.4, series = "Training") +
  autolayer(forecast.lm.sales_1.4, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.4, series = "Validation") +
  labs(title = "Dept. 4 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 5 Models:
```{r}
# Auto ARIMA model
#predictors.diff_1.1 <- diff(predictors_1.1)
#training.diff_1.1 <- diff(training_1.1)
AutoArima_1.5 <- auto.arima(training_1.5, xreg = predictors_1.5) 
summary(AutoArima_1.5)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.5 <- Arima(training_1.5, xreg = predictors_1.5, order = c(0, 0, 1), seasonal = c(0, 1, 1))
summary(arima_1.5)

# prediction on the arima
new.predictors_1.5 <- as.matrix(store_1.5["Temperature"][131:143,])
forecast.arima.sales_1.5 <- forecast(arima_1.5, xreg = new.predictors_1.5)

# plot of forecasted values
autoplot(training_1.5, series = "Training") +
  autolayer(forecast.arima.sales_1.5, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.5, series = "Validation") +
  labs(title = "Dept. 5 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.5 <- store_1.5[1:130, 6]
linear_1.5 <- tslm(training_1.5 ~ trend + season + temp_1.5)
summary(linear_1.5)

# calculating RMSE
sqrt(mean(linear_1.5$residuals^2))

# forecasting 
temp.new_1.5 <- store_1.5[131:143, 6]
forecast.lm.sales_1.5 <- forecast(linear_1.5, temp.new_1.5, h = 13)
forecast.lm.sales_1.5

# plot of forecasted values
autoplot(training_1.5, series = "Training") +
  autolayer(forecast.lm.sales_1.5, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.5, series = "Validation") +
  labs(title = "Dept. 5 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 6 Models: 
```{r}
# Auto ARIMA model
#predictors.diff_1.1 <- diff(predictors_1.1)
#training.diff_1.1 <- diff(training_1.1)
AutoArima_1.6 <- auto.arima(training_1.6, xreg = predictors_1.6) 
summary(AutoArima_1.6)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.6 <- Arima(training_1.6, xreg = predictors_1.6, order = c(2, 1, 3), seasonal = c(0, 1, 1))
summary(arima_1.6)

# prediction on the arima
new.predictors_1.6 <- as.matrix(store_1.6["Temperature"][131:143,])
forecast.arima.sales_1.6 <- forecast(arima_1.6, xreg = new.predictors_1.6)

# plot of forecasted values
autoplot(training_1.6, series = "Training") +
  autolayer(forecast.arima.sales_1.6, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.6, series = "Validation") +
  labs(title = "Dept. 6 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.6 <- store_1.6[1:130, 6]
linear_1.6 <- tslm(training_1.6 ~ trend + season + temp_1.6)
summary(linear_1.6)

# calculating RMSE
sqrt(mean(linear_1.6$residuals^2))

# forecasting 
temp.new_1.6 <- store_1.6[131:143, 6]
forecast.lm.sales_1.6 <- forecast(linear_1.6, temp.new_1.6, h = 13)
forecast.lm.sales_1.6

# plot of forecasted values
autoplot(training_1.6, series = "Training") +
  autolayer(forecast.lm.sales_1.6, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.6, series = "Validation") +
  labs(title = "Dept. 6 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 7 Models: 
```{r}
# Auto ARIMA model
#predictors.diff_1.1 <- diff(predictors_1.1)
#training.diff_1.1 <- diff(training_1.1)
AutoArima_1.7 <- auto.arima(training_1.7, xreg = predictors_1.7) 
summary(AutoArima_1.7)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.7 <- Arima(training_1.7, xreg = predictors_1.7, order = c(2, 0, 1), seasonal = c(1, 1, 0))
summary(arima_1.7)

# prediction on the arima
new.predictors_1.7 <- as.matrix(store_1.7["Temperature"][131:143,])
forecast.arima.sales_1.7 <- forecast(arima_1.7, xreg = new.predictors_1.7)

# plot of forecasted values
autoplot(training_1.7, series = "Training") +
  autolayer(forecast.arima.sales_1.7, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.7, series = "Validation") +
  labs(title = "Dept. 7 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.7 <- store_1.7[1:130, 6]
linear_1.7 <- tslm(training_1.7 ~ trend + season + temp_1.7)
summary(linear_1.7)

# calculating RMSE
sqrt(mean(linear_1.7$residuals^2))

# forecasting 
temp.new_1.7 <- store_1.7[131:143, 6]
forecast.lm.sales_1.7 <- forecast(linear_1.7, temp.new_1.7, h = 13)
forecast.lm.sales_1.7

# plot of forecasted values
autoplot(training_1.7, series = "Training") +
  autolayer(forecast.lm.sales_1.7, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.7, series = "Validation") +
  labs(title = "Dept. 7 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 8 Models: 
```{r}
# Auto ARIMA model
#predictors.diff_1.1 <- diff(predictors_1.1)
#training.diff_1.1 <- diff(training_1.1)
AutoArima_1.8 <- auto.arima(training_1.8, xreg = predictors_1.8) 
summary(AutoArima_1.8)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.8 <- Arima(training_1.8, xreg = predictors_1.8, order = c(1, 1, 1), seasonal = c(0, 1, 1))
summary(arima_1.8)

# prediction on the arima
new.predictors_1.8 <- as.matrix(store_1.8["Temperature"][131:143,])
forecast.arima.sales_1.8 <- forecast(arima_1.8, xreg = new.predictors_1.8)

# plot of forecasted values
autoplot(training_1.8, series = "Training") +
  autolayer(forecast.arima.sales_1.8, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.8, series = "Validation") +
  labs(title = "Dept. 8 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.8 <- store_1.8[1:130, 6]
linear_1.8 <- tslm(training_1.8 ~ trend + season + temp_1.8)
summary(linear_1.8)

# calculating RMSE
sqrt(mean(linear_1.8$residuals^2))

# forecasting 
temp.new_1.8 <- store_1.8[131:143, 6]
forecast.lm.sales_1.8 <- forecast(linear_1.8, temp.new_1.8, h = 13)
forecast.lm.sales_1.8

# plot of forecasted values
autoplot(training_1.8, series = "Training") +
  autolayer(forecast.lm.sales_1.8, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.8, series = "Validation") +
  labs(title = "Dept. 8 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 9 Models: 
```{r}
# Auto ARIMA model
#predictors.diff_1.1 <- diff(predictors_1.1)
#training.diff_1.1 <- diff(training_1.1)
AutoArima_1.9 <- auto.arima(training_1.9, xreg = predictors_1.9) 
summary(AutoArima_1.9)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.9 <- Arima(training_1.9, xreg = predictors_1.9, order = c(0, 1, 4), seasonal = c(0, 1, 1))
summary(arima_1.9)

# prediction on the arima
new.predictors_1.9 <- as.matrix(store_1.9["Temperature"][131:143,])
forecast.arima.sales_1.9 <- forecast(arima_1.9, xreg = new.predictors_1.9)

# plot of forecasted values
autoplot(training_1.9, series = "Training") +
  autolayer(forecast.arima.sales_1.9, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.9, series = "Validation") +
  labs(title = "Dept. 9 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.9 <- store_1.9[1:130, 6]
linear_1.9 <- tslm(training_1.9 ~ trend + season + temp_1.9)
summary(linear_1.9)

# calculating RMSE
sqrt(mean(linear_1.9$residuals^2))

# forecasting 
temp.new_1.9 <- store_1.9[131:143, 6]
forecast.lm.sales_1.9 <- forecast(linear_1.9, temp.new_1.9, h = 13)
forecast.lm.sales_1.9

# plot of forecasted values
autoplot(training_1.9, series = "Training") +
  autolayer(forecast.lm.sales_1.9, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.9, series = "Validation") +
  labs(title = "Dept. 9 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 10 Models: 
```{r}
# Auto ARIMA model
#predictors.diff_1.1 <- diff(predictors_1.1)
#training.diff_1.1 <- diff(training_1.1)
AutoArima_1.10 <- auto.arima(training_1.10, xreg = predictors_1.10) 
summary(AutoArima_1.10)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.10 <- Arima(training_1.10, xreg = predictors_1.10, order = c(1, 0, 4), seasonal = c(0, 1, 2))
summary(arima_1.10)

# prediction on the arima
new.predictors_1.10 <- as.matrix(store_1.10["Temperature"][131:143,])
forecast.arima.sales_1.10 <- forecast(arima_1.10, xreg = new.predictors_1.10)

# plot of forecasted values
autoplot(training_1.10, series = "Training") +
  autolayer(forecast.arima.sales_1.10, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.10, series = "Validation") +
  labs(title = "Dept. 10 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.10 <- store_1.10[1:130, 6]
linear_1.10 <- tslm(training_1.10 ~ trend + season + temp_1.10)
summary(linear_1.10)

# calculating RMSE
sqrt(mean(linear_1.10$residuals^2))

# forecasting 
temp.new_1.10 <- store_1.10[131:143, 6]
forecast.lm.sales_1.10 <- forecast(linear_1.10, temp.new_1.10, h = 13)
forecast.lm.sales_1.10

# plot of forecasted values
autoplot(training_1.10, series = "Training") +
  autolayer(forecast.lm.sales_1.10, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.10, series = "Validation") +
  labs(title = "Dept. 10 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 11 Models: 
```{r}
# Auto ARIMA model
#predictors.diff_1.1 <- diff(predictors_1.1)
#training.diff_1.1 <- diff(training_1.1)
AutoArima_1.11 <- auto.arima(training_1.11, xreg = predictors_1.11) 
summary(AutoArima_1.11)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.11 <- Arima(training_1.11, xreg = predictors_1.11, order = c(0, 1, 2), seasonal = c(1, 1, 0))
summary(arima_1.11)

# prediction on the arima
new.predictors_1.11 <- as.matrix(store_1.11["Temperature"][131:143,])
forecast.arima.sales_1.11 <- forecast(arima_1.11, xreg = new.predictors_1.11)

# plot of forecasted values
autoplot(training_1.11, series = "Training") +
  autolayer(forecast.arima.sales_1.11, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.11, series = "Validation") +
  labs(title = "Dept. 11 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.11 <- store_1.11[1:130, 6]
linear_1.11 <- tslm(training_1.11 ~ trend + season + temp_1.11)
summary(linear_1.11)

# calculating RMSE
sqrt(mean(linear_1.11$residuals^2))

# forecasting 
temp.new_1.11 <- store_1.11[131:143, 6]
forecast.lm.sales_1.11 <- forecast(linear_1.11, temp.new_1.11, h = 13)
forecast.lm.sales_1.11

# plot of forecasted values
autoplot(training_1.11, series = "Training") +
  autolayer(forecast.lm.sales_1.11, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.11, series = "Validation") +
  labs(title = "Dept. 11 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 12 Models: 
```{r}
# Auto ARIMA model
#predictors.diff_1.1 <- diff(predictors_1.1)
#training.diff_1.1 <- diff(training_1.1)
AutoArima_1.12 <- auto.arima(training_1.12, xreg = predictors_1.12) 
summary(AutoArima_1.12)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.12 <- Arima(training_1.12, xreg = predictors_1.12, order = c(0, 1, 5), seasonal = c(0, 1, 1))
summary(arima_1.12)

# prediction on the arima
new.predictors_1.12 <- as.matrix(store_1.12["Temperature"][131:143,])
forecast.arima.sales_1.12 <- forecast(arima_1.12, xreg = new.predictors_1.12)

# plot of forecasted values
autoplot(training_1.12, series = "Training") +
  autolayer(forecast.arima.sales_1.12, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.12, series = "Validation") +
  labs(title = "Dept. 12 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.12 <- store_1.12[1:130, 6]
linear_1.12 <- tslm(training_1.12 ~ trend + season + temp_1.12)
summary(linear_1.12)

# calculating RMSE
sqrt(mean(linear_1.12$residuals^2))

# forecasting 
temp.new_1.12 <- store_1.12[131:143, 6]
forecast.lm.sales_1.12 <- forecast(linear_1.12, temp.new_1.12, h = 13)
forecast.lm.sales_1.12

# plot of forecasted values
autoplot(training_1.12, series = "Training") +
  autolayer(forecast.lm.sales_1.12, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.12, series = "Validation") +
  labs(title = "Dept. 12 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

#### Department 13 Models: 
```{r}
# Auto ARIMA model
#predictors.diff_1.1 <- diff(predictors_1.1)
#training.diff_1.1 <- diff(training_1.1)
AutoArima_1.13 <- auto.arima(training_1.13, xreg = predictors_1.13) 
summary(AutoArima_1.13)

# ARIMA model parameters decided by the ACF and PACF plots above
arima_1.13 <- Arima(training_1.13, xreg = predictors_1.13, order = c(0, 1, 3), seasonal = c(0, 1, 1))
summary(arima_1.13)

# prediction on the arima
new.predictors_1.13 <- as.matrix(store_1.13["Temperature"][131:143,])
forecast.arima.sales_1.13 <- forecast(arima_1.13, xreg = new.predictors_1.13)

# plot of forecasted values
autoplot(training_1.13, series = "Training") +
  autolayer(forecast.arima.sales_1.13, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.13, series = "Validation") +
  labs(title = "Dept. 13 ARIMA Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

```{r}
# linear model
temp_1.13 <- store_1.13[1:130, 6]
linear_1.13 <- tslm(training_1.13 ~ trend + season + temp_1.13)
summary(linear_1.13)

# calculating RMSE
sqrt(mean(linear_1.13$residuals^2))

# forecasting 
temp.new_1.13 <- store_1.13[131:143, 6]
forecast.lm.sales_1.13 <- forecast(linear_1.13, temp.new_1.13, h = 13)
forecast.lm.sales_1.13

# plot of forecasted values
autoplot(training_1.13, series = "Training") +
  autolayer(forecast.lm.sales_1.13, alpha = 0.3, series = "Forecasts") +
  autolayer(validation_1.13, series = "Validation") +
  labs(title = "Dept. 13 LM Model Forecasted Sales",
       x = "Time",
       y = "Weekly Sales") +
    theme_classic()
```

### Model Forecasts

```{r}
accuracy(forecast.arima.sales_1.1, validation_1.1)

accuracy(forecast.arima.sales_1.2, validation_1.2)

accuracy(forecast.arima.sales_1.3, validation_1.3)

accuracy(forecast.arima.sales_1.4, validation_1.4)

accuracy(forecast.arima.sales_1.5, validation_1.5)

accuracy(forecast.arima.sales_1.6, validation_1.6)

accuracy(forecast.arima.sales_1.7, validation_1.7)

accuracy(forecast.arima.sales_1.8, validation_1.8)

accuracy(forecast.arima.sales_1.9, validation_1.9)

accuracy(forecast.arima.sales_1.10, validation_1.10)

accuracy(forecast.arima.sales_1.11, validation_1.11)

accuracy(forecast.arima.sales_1.12, validation_1.12)

accuracy(forecast.arima.sales_1.13, validation_1.13)
```

